\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

\begin{document}
    \title{Project Report : CS 7643}

    \maketitle

    \begin{abstract}
        Abstract
    \end{abstract}

    \section{Introduction/Motivation}
    The incidence of skin cancer in the U.S. is quite significant, more than 
    9,500 people are diagnosed with skin cancer every day, making it the most 
    common form of cancer in the country. It's estimated that one in five 
    Americans will develop skin cancer by the age of 70. Notably, higher 
    mortality rates are observed among men, non-Hispanic Whites, and those 
    aged over 70 \cite{Authors1}. \\
    \\
    Although various deep learning approaches have been used for 
    computer-based skin cancer detection in recent years. Most detection
    algorithms use convuolution nerual networks (CNN) to
    classify skin leasions.  To the best of our knowledge, few deep learning 
    studies on skin cancer have integrated metadata such as age, sex or leasion locations; 
    only one study has utilized the dataset incorporating the additional risk 
    factor such as race (the Caucasian and xanthous races dataset) to include these 
    meta-features \cite{Authors2, Authors3, Authors4}.\\
    \\
    In our research, we aim to incorporate these clinically investigated 
    risk factors into an enhanced model scheme \cite{Authors5}. By applying CNN transfer 
    learning to the classification task along with these additional risk 
    factors, we seek to refine the existing model architecture. This approach will improve the differentiation of malignant and 
    benign lesions, boost early detection of skin cancer, enhance diagnostic 
    accuracy, and ultimately improve clinical outcomes. \\
    \\
    Improving accuracies and early detections would be important for doctors
    patients, hospitals, and insurance companies.  Early detection can give the
    patient a 99\% survival rate \cite{Authors6}.  This also means that early
    detection results in less hospital stays, smaller operations, and less
    expenditures by patients and insurance.  Having such tools also aids
    doctors by giving them another tool to determine if a leasion is serious
    or not.  Furthermore, better accuracies will not only catch potentially malignant
    leasions but also determine if a leasion is begin and does not need to
    be removed. \\
    \\
    This research will be utilizing the HAM10000 ("Human Against Machine 10000 images")
    dataset and the ISIC 2024 dataset, both of which can be found on kaggle.com.  These datasets come with one to many images
    of leasions that can be used for training machine learning models along with
    metadata about the patient to accompany these images.  The metadata that accompanies
    the images will be the primary focus of this research as this will add new features
    in an attempt to increase accuracy. \\
    
    \section{Approach}
    Our approach

    {\small
        \bibliographystyle{ieee_fullname}
        \bibliography{report}
    }

\end{document}